The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2016-02-21 script/de/chapters/aboutcryptool.tex
Corrected some typos -- thanks to Bruce

% $Id$
% ............................................................................
%                 TEXT DER 2. SEITE (Überblick)
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% --------------------------------------------------------------------------
% HACK to fix warning "destination with the same identifier .. has already been used, ...":
\makeatletter \renewcommand{\thepage}{~\csname @roman\endcsname \c@page~} \makeatother
\clearpage\phantomsection
% HACK to fix warning "destination with the same identifier .. has already been used, ...":
\makeatletter \renewcommand{\thepage}{\csname @roman\endcsname \c@page} \makeatother
\addcontentsline{toc}{chapter}{Überblick über den Inhalt des CrypTool-Skripts}
\chapter*{Überblick über den Inhalt des CrypTool-Skripts}

@@

In diesem {\em Skript zu den CrypTool-Programmen} \index{CrypTool} finden Sie
eher mathematisch orientierte Informationen zum Einsatz von
kryptographischen Verfahren. Zu einigen Verfahren gibt es Beispielcode,
geschrieben für das Computer-Algebra-System {\bf SageMath}\index{SageMath}
(siehe Anhang~\ref{s:appendix-using-sage}).
Die Hauptkapitel sind von verschiedenen {\bf Autoren} verfasst
(siehe Anhang~\ref{s:appendix-authors}) %\hyperlink{appendix-authors}{Autoren}
und in sich abgeschlossen. Am Ende der meisten Kapitel finden Sie
Literaturangaben und Web-Links.
Die Kapitel wurden reichlich mit {\em Fußnoten} versehen, in denen auch darauf verwiesen
wird, wie man die beschriebenen Funktionen in den verschiedenen CrypTool-Programmen 
aufruft.

@@

Ein großer Teil des Skripts ist dem faszinierenden Thema der
{\bf Primzahlen} (Kapitel \ref{Label_Kapitel_Primes})
% \hyperlink{Kapitel_2}{{\bf Primzahlen}} 
gewidmet.
Anhand vieler Beispiele wird in die {\bf modulare Arithmetik} und die 
{\bf elementare Zahlentheorie} (Kapitel \ref{Chapter_ElementaryNT})
% \hyperlink{Chapter_ElementaryNT} {{\bf elementare Zahlentheorie}} 
eingeführt. Die Eigenschaften des {\bf RSA-Verfahrens} bilden einen Schwerpunkt.

@@

Während die CrypTool-\textit{eLearning-Programme}\index{eLearning} eher den
praktischen Umgang motivieren und vermitteln, dient das \textit{Skript} dazu, 
dem an Kryptographie Interessierten ein tieferes Verständnis für die 
implementierten mathematischen Algorithmen zu vermitteln -- und das 
didaktisch mög"-lichst gut nachvollziehbar.

@@

\enlargethispage{0.5cm}
Wie auch bei dem E-Learning-Programm CrypTool\index{CrypTool} wächst 
die Qualität des Skripts mit den Anregungen und Verbesserungsvorschlägen 
von Ihnen als Leser. Wir freuen uns über Ihre Rück"-mel"-dung.

>>>>

% $Id$
% ............................................................................
%                 TEXT DER 2. SEITE (Überblick)
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% --------------------------------------------------------------------------
% HACK to fix warning "destination with the same identifier .. has already been used, ...":
\makeatletter \renewcommand{\thepage}{~\csname @roman\endcsname \c@page~} \makeatother
\clearpage\phantomsection
% HACK to fix warning "destination with the same identifier .. has already been used, ...":
\makeatletter \renewcommand{\thepage}{\csname @roman\endcsname \c@page} \makeatother
\addcontentsline{toc}{chapter}{Überblick über den Inhalt des CrypTool-Buchs}
\chapter*{Überblick über den Inhalt des CrypTool-Buchs}

@@

In diesem {\em Buch zu den CrypTool-Programmen} \index{CrypTool} finden Sie
eher mathematisch orientierte Informationen zum Einsatz von
kryptographischen Verfahren. Zu einigen Verfahren gibt es Beispielcode,
geschrieben für das Computer-Algebra-System {\bf SageMath}\index{SageMath}
(siehe Anhang~\ref{s:appendix-using-sage}).
Die Hauptkapitel sind von verschiedenen {\bf Autoren} verfasst
(siehe Anhang~\ref{s:appendix-authors}) %\hyperlink{appendix-authors}{Autoren}
und in sich abgeschlossen. Am Ende der meisten Kapitel finden Sie
Literaturangaben und Web-Links.
Die Kapitel wurden reichlich mit {\em Fußnoten} versehen, in denen auch darauf verwiesen
wird, wie man die beschriebenen Funktionen in den verschiedenen CrypTool-Programmen 
aufruft.

@@

Ein großer Teil des Buchs ist dem faszinierenden Thema der
{\bf Primzahlen} (Kapitel \ref{Label_Kapitel_Primes})
% \hyperlink{Kapitel_2}{{\bf Primzahlen}} 
gewidmet.
Anhand vieler Beispiele wird in die {\bf modulare Arithmetik} und die 
{\bf elementare Zahlentheorie} (Kapitel \ref{Chapter_ElementaryNT})
% \hyperlink{Chapter_ElementaryNT} {{\bf elementare Zahlentheorie}} 
eingeführt. Die Eigenschaften des {\bf RSA-Verfahrens} bilden einen Schwerpunkt.

@@

Während die CrypTool-\textit{eLearning-Programme}\index{eLearning} eher den
praktischen Umgang motivieren und vermitteln, dient das \textit{Buch} dazu, 
dem an Kryptographie Interessierten ein tieferes Verständnis für die 
implementierten mathematischen Algorithmen zu vermitteln -- und das 
didaktisch mög"-lichst gut nachvollziehbar.

@@

\enlargethispage{0.5cm}
Wie auch bei dem E-Learning-Programm CrypTool\index{CrypTool} wächst 
die Qualität des Buchs mit den Anregungen und Verbesserungsvorschlägen 
von Ihnen als Leser. Wir freuen uns über Ihre Rück"-mel"-dung.

### 2016-02-21 script/en/chapters/aboutcryptool.tex
Corrected some typos -- thanks to Bruce

% --------------------------------------------------------------------------
% HACK to fix warning "destination with the same identifier .. has already been used, ...":
\makeatletter \renewcommand{\thepage}{~\csname @roman\endcsname \c@page~} \makeatother
\clearpage\phantomsection
% HACK to fix warning "destination with the same identifier .. has already been used, ...":
\makeatletter \renewcommand{\thepage}{\csname @roman\endcsname \c@page} \makeatother
\addcontentsline{toc}{chapter}{Overview about the Content of the CrypTool Script}
\chapter*{Overview about the Content of the CrypTool Script}

\parskip 4pt
%\vskip +12 pt
The rapid spread of the Internet has lead to intensified research in the
technologies involved, especially within the area of cryptography where a good
deal of new knowledge has arisen.

In this {\em script accompanying the CrypTool programs} \index{CrypTool}
you will find predominantly mathematically oriented information on using
cryptographic procedures. Also included are many sample code pieces written in the
computer algebra system {\bf SageMath}\index{SageMath} (see appendix~\ref{s:appendix-using-sage}).
The main chapters have been written by various {\bf authors}
(see appendix~\ref{s:appendix-authors}) %\hyperlink{appendix-authors}{authors}
and are therefore independent from one another. At the end of most chapters
you will find references and web links.
The sections have been enriched with many {\em footnotes}. Within the footnotes
you can see where the described functions can be called in the different CrypTool
versions.

@@

Big parts of this script are dedicated to the fascinating topic of 
{\bf prime numbers} (chap. \ref{Label_Kapitel_Primes}).
%\hyperlink{Kapitel_2}{{\bf prime numbers}}. 
Using numerous examples, {\bf modular arithmetic} and 
{\bf elementary number theory} (chap. \ref{Chapter_ElementaryNT})
are introduced. The features of the {\bf RSA procedure} are a key aspect.

@@

Whereas the CrypTool \textit{e-learning programs}\index{e-learning} motivate
and teach you how to use cryptography in practice, the \textit{script} provides
those interested in the subject with a deeper understanding of the mathematical
algorithms used -- trying to do it in an instructive way.

@@

\enlargethispage{12pt}
As with the e-learning program CrypTool\index{CrypTool}, the quality of the 
script is enhanced by your suggestions and ideas for improvement. 
We look forward to your feedback.

>>>>

% --------------------------------------------------------------------------
% HACK to fix warning "destination with the same identifier .. has already been used, ...":
\makeatletter \renewcommand{\thepage}{~\csname @roman\endcsname \c@page~} \makeatother
\clearpage\phantomsection
% HACK to fix warning "destination with the same identifier .. has already been used, ...":
\makeatletter \renewcommand{\thepage}{\csname @roman\endcsname \c@page} \makeatother
\addcontentsline{toc}{chapter}{Overview about the Content of the CrypTool Book}
\chapter*{Overview about the Content of the CrypTool Book}

\parskip 4pt
%\vskip +12 pt
The rapid spread of the Internet has led to intensified research in the
technologies involved, especially within the area of cryptography where a good
deal of new knowledge has arisen.

In this {\em book accompanying the CrypTool programs} \index{CrypTool}
you will find predominantly mathematically oriented information on using
cryptographic procedures. Also included are many sample code pieces written in the
computer algebra system {\bf SageMath}\index{SageMath} (see appendix~\ref{s:appendix-using-sage}).
The main chapters have been written by various {\bf authors}
(see appendix~\ref{s:appendix-authors}) %\hyperlink{appendix-authors}{authors}
and are therefore independent from one another. At the end of most chapters
you will find references and web links.
The sections have been enriched with many {\em footnotes}. Within the footnotes
you can see where the described functions can be called in the different CrypTool
versions.

@@

Big parts of this book are dedicated to the fascinating topic of 
{\bf prime numbers} (chap. \ref{Label_Kapitel_Primes}).
%\hyperlink{Kapitel_2}{{\bf prime numbers}}. 
Using numerous examples, {\bf modular arithmetic} and 
{\bf elementary number theory} (chap. \ref{Chapter_ElementaryNT})
are introduced. The features of the {\bf RSA procedure} are a key aspect.

@@

Whereas the CrypTool \textit{e-learning programs}\index{e-learning} motivate
and teach you how to use cryptography in practice, the \textit{book} provides
those interested in the subject with a deeper understanding of the mathematical
algorithms used -- trying to do it in an instructive way.

@@

\enlargethispage{12pt}
As with the e-learning program CrypTool\index{CrypTool}, the quality of the 
book is enhanced by your suggestions and ideas for improvement. 
We look forward to your feedback.
